A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-07-16 paper/paper.tex
Some rewording

\section{Semi-simplicial and semi-cubical sets\label{sec:nu}}
In this section, we generalize semi-simplicial and semi-cubical sets to, what we call, $\nu$-sets, subsuming the earlier definitions. However, we also explicitly work out the cases of semi-simplicial and semi-cubical sets, in a way that is similar to a previous art~(\citeyear{aitchison86}).

\subsection*{Augmented semi-simplicial sets}
Augmented semi-simplicial sets are defined similarly to semi-simplicial sets, except that the connected components are additionally dependent on a ``color''. Conversely, semi-simplicial sets can be seen as augmented semi-simplicial sets over a singleton set of colors.

>>>>

\section{Semi-simplicial and semi-cubical sets\label{sec:nu}}
In this section, we generalize semi-simplicial and semi-cubical sets to, what we call, $\nu$-sets, subsuming the earlier definitions. We start by first explicitly working out the cases of semi-simplicial and semi-cubical sets. %, in a way that is similar to a previous art~(\citeyear{aitchison86}).

\subsection*{Augmented semi-simplicial sets}
Augmented semi-simplicial sets are defined similarly to semi-simplicial sets, except that the connected components are additionally dependent on a ``color''. Conversely, semi-simplicial sets can be seen as augmented semi-simplicial sets over the singleton set of one fixed color.
